\documentclass{article}
\usepackage{graphicx}
\usepackage[margin=1in]{geometry}
\usepackage{minted}

\begin{document}

\title{CS102: Week 1}

\maketitle

\section*{Write Hello World}
\begin{enumerate}
\item Open a plaintext editor (notepad, notepad++)
\item Type the following in the editor:
\begin{minted}{c++}
#include <iostream>
int main(){
	std::cout<<"Hello World!"<<std::endl;
	return 0;
}
\end{minted}
\item Save the file as hello.cpp on the desktop
\item Open a terminal (command prompt in Windows)
\item Change into the directory(folder) containing hello.cpp by typing the following into the terminal: 
\begin{minted}{bat}
cd  \Users\username\Desktop
\end{minted}
Replace \texttt{username} with the username used to log into the computer.

\item Compile by typing the following into the terminal:
\begin{minted}{bat}
g++ -Wall -o hello hello.cpp
\end{minted}
Note: \texttt{hello} is an arbitrary name, and the executable and source names do not need to match

\item Run the executable file by typing the following into the terminal:
\begin{minted}{bat}
hello.exe
\end{minted}

\end{enumerate}
\pagebreak
\section*{Debug Hello World}
\begin{enumerate}
\item Type the following in the editor:
\begin{minted}{c++}
include <iostream>
	
int main(){
	cout<<"Hello World!<<std::endl;
	return 0
}
\end{minted}
\item Save it and compile
\\
\item Answer the following questions:
	\begin{enumerate}
		\item What does the error message say?
		\item What line is the error message on?
	\end{enumerate}
\item Fix the file and compile again
\end{enumerate}

\section*{Modify Hello World}
You will work in pairs for this task. 
\begin{enumerate}
\item Choose one person as the programmer and the other as the onlooker. 
\item The programmer should change hello.cpp so that it prints-out "Hello my name is \textit{name}!" while the onlooker helps. 
\item Save the file as \textit{name}.cpp, compile, and run. 
\item Switch roles. 
\item Repeat step two, with the new programmer changing the hello world program as described above and the onlooker helping. 
\item Save the file as \textit{name}.cpp, compile, and run.
\end{enumerate}
\textbf{Note:} Replace \textit{name} with your name! 



\end{document}